A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-10 docs/methods/erosion_methods.tex
NM

\paragraph{Related Work}
In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}. The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.). Another advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.  In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations. Thus, rather than a single, mobile body as considered in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies. Although the traction formulation has several attractive features, we will instead employ a standard double-layer formulation, since it allows us to easily calculate bulk quantities such as vorticity, pressure, and velocity, that will facilitate our understanding of the erosion.

>>>>

\paragraph{Related Work}
In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}. The flexibility of their formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.). Another advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.  In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations. Thus, rather than a single, mobile body as considered in \cite{mit-spa2016}, we will simulate the erosion of many, immobile bodies. Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities, such as vorticity, pressure, and velocity, that will assist our understanding of the erosion process.
